Analysing the effect of land-use type on the proportion of scouts

### 2021-10-23 analysis/landuse_effect_prop_scouts.Rmd
started preentation of work in this analysis folder

ggplot(data = plotdata, aes(x = Comp_.1, y = p)) +
  geom_point() +
  geom_line(data = newdat, aes(x = Comp_.1, y = fit)) +
  xlim(min(-2.5), max(3.))
```

@@

plotdata$LU = ""
plotdata$LU[1:10] = "Rural"
plotdata$LU[11:20] = "Urban"

ggplot(data = plotdata,
  aes(x = Comp_.1 + Comp_.2 + Comp_.3 + Comp_.4, y = p)) +
  geom_point(aes(colour = LU)) +
  geom_rug(aes(colour = LU)) +
  scale_color_manual(values = c("Rural" = "black", "Urban" = "red")) +
  geom_line(data = newdat, aes(x = Comp_.1 + Comp_.2 + Comp_.3 + Comp_.4, y = fit)) +
  xlim(min(-5.5), max(5.5))

ggplot(data = plotdata,
  aes(x = LU, y = Comp_.1 + Comp_.2 + Comp_.3 + Comp_.4)) +
  geom_boxplot(aes(group = LU))

```

>>>>

ggplot(data = plotdata, aes(x = Comp_.1, y = p)) +
  geom_point() +
  geom_line(data = newdat, aes(x = Comp_.1, y = fit)) +
  xlim(min(-2.5), max(3.))

ggsave("analysis/results/prop_scout_lu_analysis/rural_pls_p1.png")
```

@@

plotdata$LU <- ""
plotdata$LU[1:10] <- "Rural"
plotdata$LU[11:20] <- "Urban"

ggplot(
  data = plotdata,
  aes(x = Comp_.1 + Comp_.2 + Comp_.3 + Comp_.4, y = p)
) +
  geom_point(aes(colour = LU)) +
  geom_rug(aes(colour = LU)) +
  scale_color_manual(values = c("Rural" = "black", "Urban" = "red")) +
  geom_line(data = newdat, aes(x = Comp_.1 + Comp_.2 + Comp_.3 + Comp_.4, y = fit)) +
  xlim(min(-5.5), max(5.5))

ggplot(
  data = plotdata,
  aes(x = LU, y = Comp_.1 + Comp_.2 + Comp_.3 + Comp_.4)
) +
  geom_boxplot(aes(group = LU))
```
